Hijacking Simulators with Universal Probabilistic Programming

### 2019-08-08 paper/learning/notes.tex
added todo list in section 4

\subsection{Ground truth}

>>>>

\paragraph{TODO list}
\begin{itemize}
  \item Implement baselines
  \item Implement plotting scripts and evaluation scripts
  \item testing code and infrastructure
  \item litrature review on any methods to learn rejection sampling methods, 
  and conditional density estimation. See this paper for kernel approximation 
  methods~\cite{erraqabi2016pliable}. In addition to the methods listed in the 
  rejection sampling subsection. 
\end{itemize}
\subsection{Ground truth}
